Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States

### 2017-07-11 doc/manuscript/manuscript.Rmd
nitpciky changes

### Analysis of Molecular Variance

@@

### Discriminant Analysis of Principal Components

@@

Nearly all populations showed evidence for linkage (\@ref(fig:iatab)), which serves as evidence for clonal reproduction or other forms of non-random mating. 
The only exceptions are CA and Australia. Both of these populations showed only moderate significance (P < 0.05) with $\bar{r}_d$ values of 0.03 and 0.12, respectively.

>>>>

### Analysis of Molecular Variance {-}

@@

### Discriminant Analysis of Principal Components {-}

@@

Nearly all populations showed evidence for linkage (Table \@ref(tab:iatab)), which serves as evidence for clonal reproduction or other forms of non-random mating. 
The only exceptions are CA and Australia. Both of these populations showed only moderate significance (P < 0.05) with $\bar{r}_d$ values of 0.03 and 0.12, respectively.
